Implementation of Concurrent Hash Tables in Java

### 2022-04-29 paper.tex
Finished the Algorithm's Section

\begin{lstlisting}[language={Java},caption=Source code for the course-grain search() method.,captionpos=b,breaklines=true,frame=single]
public synchronized boolean search(int item) {
    int key = hash(item);
    int i = 0;
    int new_key = (key + i) % ARR_SIZE;
    // Quadratically probe for the item
    // Dirty indices are considered to be a collision, the item may of been probed
    // farther down
    while (!cleans[new_key]) {
        if (table[new_key] == null) {
        } else if (item == table[new_key]) {
            return true;
        }
        i++;
        new_key = (new_key + i) % ARR_SIZE;
        if (i >= ARR_SIZE)
            break;
    }

@@

    // Quadratically probe for the item
    // Dirty indices are considered to be a collision, the item may of been probed
    // farther down
    while (!cleans[new_key]) {
        if (item == table[new_key]) {
            table[new_key] = null;
            break;
        }
        i++;
        new_key = (new_key + i) % ARR_SIZE;
    }

@@

>>>>

\begin{lstlisting}[language={Java},caption=Source code for the course-grain search() method.,captionpos=b,breaklines=true,frame=single]
public synchronized boolean search(int item) {
    int key = hash(item);
    int i = 0;
    int new_key = (key + i) % ARR_SIZE;
    // Linearly probe for the item
    // Dirty indices are considered to be a collision, the item may of been probed
    // farther down
    while (!cleans[new_key]) {
        if (table[new_key] == null) {
        } else if (item == table[new_key]) {
            return true;
        }
        i++;
        new_key = (new_key + i) % ARR_SIZE;
        if (i >= ARR_SIZE)
            break;
    }

@@

    // Linearly probe for the item
    // Dirty indices are considered to be a collision, the item may of been probed
    // farther down
    while (!cleans[new_key]) {
        if (item == table[new_key]) {
            table[new_key] = null;
            break;
        }
        i++;
        new_key = (new_key + i) % ARR_SIZE;
    }

@@

"Listing 3" contains the code for coarse-grain locking hash table's \verb|remove()| method. The method is used to remove the value given to the method from the
hash table. It begin's by calculating the initial key for that value by utilizing the hash table's \verb|hash()| method. After it calculates the key, the method
makes a call to \verb|search()| to see if the value is in the hash table. If the value has not been added, then there is no way to remove it and the \verb|remove()|
function returns false, due to the impossible nature of removing it. Now that the \verb|remove()| method is aware that the value it is trying to remove
exists within the hash table, it needs to find and remove the value. It does this by utilizing the same exact loop from the \verb|search()| function, which 
revolves around testing locations in the \verb|clean| to see if there has ever been data at this memory location in the hash table. The loop will continually check
every single location that the data could have been placed into until it finds it, which the method is guaranteed to do as the call to \verb|search()| indicated
that the value was in the array. Once the memory location with the value has been found, it is set to null in order to remove it from memory. After that, \verb|remove()|
will decrease the \verb|capacity| variable, so that the hash table knows how many values are stored inside of it, and then returns true to indicate that the value
was removed from the table successfully.
